\documentclass[10pt,letterpaper]{article}
\usepackage{graphicx}
\usepackage{url}
\usepackage{color}
\usepackage[dvipsnames]{xcolor}
\usepackage{enumerate}
\usepackage{fancyhdr}
\usepackage[resetlabels]{multibib}
\usepackage{multicol}
\usepackage{tikz}

%\usepackage{showframe}

% Set margins.
\oddsidemargin=-0.50in
\textwidth=7in
\topmargin=-1.5in
\textheight=10.0in

% Define colors.
\definecolor{addresscolor}{rgb}{0.2,0.2,0.2}
\definecolor{datecolor}{rgb}{0.5,0.5,0.5}

% Turn off page numbering
\pagestyle{fancy}
\fancyhf{}
\lfoot{\datestyle Gabriel De la Parra}
\rfoot{\datestyle November 2015}

% Set parameters and content.
\newcommand{\namestyle}{\Huge \scshape}
\newcommand{\deptstyle}{\small \rmfamily \scshape}
\newcommand{\addressstyle}{\color{addresscolor} \footnotesize \rmfamily \upshape}
\newcommand{\datestyle}{\color{datecolor} \footnotesize \rmfamily \upshape}

% Remove list labels.
\renewcommand{\labelitemi}{}
\renewcommand{\labelitemii}{}

\makeatletter
\renewcommand\subparagraph{\@startsection{subparagraph}{5}{\parindent}%
	{3.25ex \@plus1ex \@minus .2ex}%
	{0.75ex plus 0.1ex}% space after heading
	{\normalfont\normalsize\bfseries}}
\makeatother


\begin{document}
\begin{tikzpicture}[remember picture,overlay]
\node[xshift=0cm] at (current page.south west)
{\begin{tikzpicture}[remember picture, overlay] 
	\fill[black!10!white] (7.5,0) rectangle (0,\paperheight);
	\end{tikzpicture}
};
\end{tikzpicture}


\begin{flushright}
\namestyle \color{MidnightBlue} Gabriel de la parra \\[0.1em]
\deptstyle \color{black} Electrical Engineer $\cdot$ Computer Scientist \\[0.5em]
\addressstyle 
Address: Huerfanos 2291, Santiago, Chile
\\Phone: +56 9 622 611 03
\\Email: ignacio.delaparra@gmail.com
\\Web: http://gabrieldelaparra.github.io
\end{flushright}

\begin{minipage}{0.3\textwidth} 
		  
\section*{\color{MidnightBlue} Education}

\subparagraph{MSc. Computer Science}
Universidad de Chile
\\Chile
\\2015 - Present

\subparagraph{MSc. Electrical Engineering}
Automation and Control
\\Technische Universit\"{a}t Dresden
\\Germany
\\2010-2011

\subparagraph{MSc. Electrical Engineering}
Process Automation
\\Universidad de Santiago de Chile
\\Chile
\\2007-2009

\subparagraph{BSc Electrical Engineering}
Universidad de Santiago de Chile
\\Chile
\\2004-2007

\section*{\color{MidnightBlue} Computer Skills}
\subparagraph{Programming}
C\#, Java, \LaTeX, HTML/XML, Matlab, VBS, Assembler, SQL, 
\subparagraph{Office}
Access, VisualStudio, Visio, Project

\section*{\color{MidnightBlue} Languages}
\subparagraph{Spanish}
\subparagraph{English}
\subparagraph{German}


\end{minipage}
\begin{minipage}{0.7\textwidth} 
\begin{flushright}
\section*{\color{MidnightBlue} Professional Experience}	
\subparagraph{\large{Research and Development Engineer}}
\textbf{ABB S.A. $\bullet$ 2013 - Present $\bullet$ Chile}
\\\textit{Power System Substation Automation, Protection and Control Division}
\\[1em]\textbf{Automation Tools for Productivity Improvement}
\\Substation Electrical Drawings
\\Project Documentation
\\IEDs Configuration
\\SCADA Configuration
\\Team Infraestructure Productivity
\\[2em]	
\subparagraph{\large{Project Engineer}}
\textbf{ABB S.A. $\bullet$ 2011 - Present $\bullet$  Chile}
\\\textit{Power System Substation Automation, Protection and Control Division}
\\[1em]\textbf{Projects Responsabilities}
\\Control and Protection Schemes design and development
\\Substation's Electrical Drawings Design and Draft
\\Project Documentation design and development
\\Control and Protection Series IEDs configuration
\\Technical meetings with customers
\\[2em]			
\subparagraph{\large{Research and Development Intern}}
\textbf{Parker Hannifin GmbH $\bullet$ 2010 - 2011 $\bullet$  Germany}
\\\textit{Europe's SensoControl R\&D Division}
\\[1em]\textbf{USB - IOLink interface prototype}
\\Circuit/PCB design, construction and testing.
\\System Design based on the IOLink Standard. 
\\Hardware and software design, construction, programming, testing.
\\COM Wrappers for unmanaged C libraries.
\\LABView interface design and programming for device's production chain.
\\Prototypes’ HMI simulators design and develpment for analysis and testing.
\\Project documentation.

\end{flushright}

\end{minipage}
	
	
\end{document}
